### 2015-03-02 fundamentals/impl.tex
addresses confusion about aggregate nuclides by deleting the phrase."

The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
objects. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.

>>>>

The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
objects. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, etc. (i.e., a
\Class{Composition}), in a material. The
\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.
